\documentclass{template/faangpath}

% Document margins
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Leonardo Murça}
\address{+55(31) 99246-1009 \\ Belo Horizonte, Brazil} 
\address{
	\href{mailto:leo@leomurca.xyz}{leo@leomurca.xyz} \\ 
	\href{https://linkedin.com/in/leonardoamurca}{linkedin.com/in/leonardoamurca} \\ 
	\href{www.faangpath.com}{www.leomurca.xyz}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\begin{rSection}{SUMMARY}

Software engineer with 4+ years experience developing Android apps for the health care 
and entertainment industries. Skilled at developing secure, reliable Android applications. 
Advanced technical skills include Android Jetpack, Bluetooth Integration, UI Tests, 
ExoPlayer integration and Coroutines.

\end{rSection}


\begin{rSection}{EXPERIENCE}

\textbf{Android Developer} \hfill Jan 2024 - current\\
ArcTouch LLC @ Internal Projects\hfill \textit{Florianopolis, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Mentored and trained a Junior Android Developer.
     \item Contributed to the company blog writing blog posts about Android Development.
     \item Delved deeper into Jetpack Compose, ExoPlayer and Coroutines study and PoCs.
 \end{itemize}

\textbf{Android Developer} \hfill May 2022 - Dec 2023\\
ArcTouch LLC @ Disney Client\hfill \textit{Florianopolis, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved 100\% of migration of automated tests using Espresso to UIAutomator.
     \item Increased in 70\% test coverage in the codebase. 
     \item Delivered sensitive features like deeplinks integration and onboarding tooltips.
     \item Helped on the migration of the xml layouts to Jetpack Compose.
 \end{itemize}
 
\textbf{Android Developer}\hfill Feb 2020 - May 2022\\
	CI\&T @ Confidential Health Care Company Client \hfill \textit{Belo Horizonte, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Identified and fixed bottlenecks in the pipeline caused by Espresso Flaky Tests.
    \item Designed technical features through ownership of technical refinements. 
		\item Crafted innovative solutions for user stories, contributing to the seamless execution of projects.
		\item Established and documented key components of the application's technical specifications, 
			ensuring clarity and precision in project development.
	 	\item Engineered a high-impact framework from inception, streamlining communication between the 
			application and OS Bluetooth layers. Leveraged Java programming to seamlessly integrate with 
			the Bluetooth Layer, ensuring efficient connectivity and robust functionality. 
		\item Assumed responsibility for leading agile ritual sessions such as PDCA, facilitating the 
			identification of development process gaps and driving continuous improvement initiatives.
		\item Served as a mentor in an Android Bootcamp program, imparting expertise in Espresso Tests 
			and SOLID principles to train newcomers, fostering skill development and knowledge sharing within the team.
		\item Designed and implemented comprehensive test cases throughout the quality assurance (QA) phase, 
			ensuring thorough testing and validation of Android applications.
	\end{itemize}

\textbf{Web Front-End Developer}\hfill Aug 2018 - Dec 2020\\
	Queima Diaria \hfill \textit{Belo Horizonte, Brazil}
 \begin{itemize}
    \itemsep -3pt {} 
    \item Initiated career as a software engineer under the guidance of senior mentors, 
		gaining valuable insights and hands-on experience in Web Development.    
		\item Delivered a MVP TV App Streaming Client supporting LG and Samsung OS.
		\item Delivered an integration with Vimeo Player for a livestream feature used by
			more than 200.000 active users.
	\end{itemize}

\end{rSection} 

\newpage
%----------------------------------------------------------------------------------------
% SKILLS 
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

{\bf Language Skills:} Fluent English, Fluent Portuguese, Intermediate Spanish.

{\bf Technical Skills:} Java, Kotlin, MVVM, MVP, MVI, Clean Architecture, RESTful APIs, Retrofit, 
SQLite, Room Persistence Library, JUnit, Espresso, Dagger 2, Hilt, Koin, Jenkins, GitLab,
Scrum, Kanban, Android Studio, SDK Manager, XML, JSON, Performance Optimization, Android Profiler

{\bf Soft Skills:} Strong problem-solving abilities, effective communication skills for collaborating, 
with cross-functional teams, adaptability to rapidly changing environments and technologies,
attention to detail in code review and debugging, time management and prioritization to meet project 
deadlines, openness to receiving and providing constructive feedback, eagerness to learn and stay 
updated with the latest trends and technologies in Android development.



\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Information Systems}, IFMG University \hfill {2018 - 2024}

{\bf Computer Technician}, IFMG University\hfill {2015 - 2017}

\end{rSection}

\end{document}
